An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-10 paper/paper.tex

% TODO: Ask Sarkozy/Mihaly if they think keeping this section in is worth it.
\subsection{File Chunking}
The format in which files are stored can have an effect on the efficiency of the system. At first, backing up each file as a whole might seem like the obvious choice, since files are only useful in their entirety. However, the creators of the P2P backup systems pStore and PeerStore have shown that there are  split files up into chunks, rather than distributing files to peers in their entirety. They also use special files, called File Block Lists in pStore and Descriptors in PeerStore, that list which blocks belong to the file and where to find them in the network. This has the benefit of having data units be a fixed size that will be easy to store for any node. For example, if a peer needs to store a 10GB file, it does not need to find a peer capable of storing 10GB (which might be rare); rather, it needs to find $file\_size/chunk\_size*number\_of\_replicas$ peers. Although lowering the chunk size will increase the chances of finding a peer to store on, it is important to choose a reasonable chunk size, as using more nodes for storage will add more overhead in finding those nodes.

>>>>

% TODO: Ask Sarkozy/Mihaly if they think keeping this section in is worth it.
\subsection{File Chunking} \label{sec:filechunking}
The format in which files are stored can have an effect on the efficiency of the system. At first, backing up each file as a whole might seem like the obvious choice, since files are only useful in their entirety. However, the creators of the P2P backup systems pStore and PeerStore have shown that there are benefits to splitting files up into chunks, rather than distributing complete files to peers. In these systems, this is accomplished by creating two types of files: a "file block", which contains a section of the original file, and a "file block list", which contains information on which file blocks compose the original file and how to order them. They also use special files, called File Block Lists in pStore and Descriptors in PeerStore, that list which blocks belong to the file and where to find them in the network. This has the benefit of having data units be a fixed size that will be easy to store for any node. For example, if a peer needs to store a 10GB file, it does not need to find a peer capable of storing 10GB (which might be rare); rather, it needs to find $file\_size/chunk\_size*number\_of\_replicas$ peers. Although lowering the chunk size will increase the chances of finding a peer to store on, it is important to choose a reasonable chunk size, as using more nodes for storage will add more overhead in finding those nodes.
